Dataset-level report

### 2020-01-20 analysis/reports/dat_report_template.Rmd
add fxn to assign manips to macd

>>>>

```{r manip}

if(this_dataset == "macdb") {
  all_di_manip <- readd(all_di_manip, cache = cache)

  manip_skew_plot <- ggplot(data = all_di_manip, aes(x = treatment, y = skew_percentile, group = studyID)) +
    geom_line() +
    theme_bw()

  manip_skew_plot

  manip_simpson_plot <- ggplot(data = all_di_manip, aes(x = treatment, y = simpson_percentile, group = studyID)) +
    geom_line() +
    theme_bw()

  manip_simpson_plot

}
